State of the Practice for Lattice Boltzmann Method Software

### 2022-01-10 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revised RQs

@@

\begin{enumerate}
	\item What artifacts are present in current LBM packages? 
	\item What tools (development, dependencies, project management) are used by
	current LBM solvers?
	\item What principles, processes, and methodologies are used in the development
	of current LBM packages?
	\item What are the pain points for developers working on LBM software
	projects?  What aspects of the existing processes, methodologies and tools do
	they consider as potentially needing improvement?  How should processes,
	methodologies and tools be changed to improve software development and
	software quality?
	\item For LBM software developers, what specific actions are taken to
	address the following:
	\begin{enumerate}
		\item installability
		\item correctness and verifiability
		\item reliability
		\item robustness
		\item performance
		\item usability
		\item maintainability
		\item modifiability
		\item reusability
		\item understandability
		\item traceability
		\item visibility and transparency
		\item reproducibility
		\item unambiguity
	\end{enumerate} 
	\item How does software designated as high quality by this methodology
	compare	with top rated software by the community?
\end{enumerate}

>>>>

\newcounter{rqnum} %research question number
\newcommand{\rqtherqnum}{RQ`'\therqnum}
\newcommand{\rqref}[1]{RQ\ref{#1}}

@@

\begin{enumerate}
	\item[RQ\refstepcounter{rqnum}\therqnum \label{RQ_WhatProjects}:] What LBM
	software projects exist, with the constraint that the source code must be
	available for all identified projects?
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_HighestQuality}:] Which
	of the projects identified in \rqref{RQ_WhatProjects} follow current best
	practices, based on evidence found by experimenting with the software and
	searching the artifacts available in each project's repository?
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareHQ2Popular}:] How
	similar is the list of top projects identified in \rqref{RQ_HighestQuality}
	to the most popular projects, as viewed by the scientific community?
    \item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareArtifacts}:] How
	do LBM projects compare to research software in general with respect to
	the artifacts present in their repositories?
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareToolsProjMngmnt}:]
	How do LBM projects compare to research software in general with
	respect to the use of tools for:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareToolsProjMngmnt}.a] development; and,
		\item [\rqref{RQ_CompareToolsProjMngmnt}.b] project management?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_PainPoints}:] What are
	the pain points for developers working on LBM software projects? 
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_ComparePainPoints}:] How
	do the pain points of developers from LBM compare to the pain points
	for research software in general?
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Concerns}:] For LBM
	developers:
	\begin{enumerate} 
		\item [\rqref{RQ_Concerns}.a] what software development concerns exist; and,
		\item [\rqref{RQ_Concerns}.b] what specific actions are taken to address
		these concerns?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareConcerns}:]
	Compared to research software in general, how is LBM software (as answered
	in \rqref{RQ_Concerns}) different with respect to:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareConcerns}.a] software development concerns?; and,
		\item [\rqref{RQ_CompareConcerns}.b] specific actions taken to address
		concerns?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Future}:] What actions
	could be employed by future LBM developers to address the concerns
	identified in \rqref{RQ_Concerns} and the pain points found in
	\rqref{RQ_PainPoints}?

\end{enumerate}
